\LARGE \bf Simultaneous Coordinate Calibrations by Solving the AX=YB Problem without Correspondence*

### 2015-06-28 Tex_AXYB/paper.tex
need to be revised by qianli

\begin{center}
\begin{figure}
\centering
\includegraphics[width=2.6in]{fig3.eps}
\caption{
$Bs$ are randomly generated using  $B_i=B_{init}exp(\widehat{\mathbf{x}})$,$\mathbf{x}=(x_1,\dots,x_6)^T $ where $x_i \sim \mathcal{N}(0,0.1)$.
}
\label{fig2}
\end{figure}
\end{center}

\begin{figure}
\centering
\includegraphics[width=2.6in,bb=84 202 501 581]{fig2.eps}
\caption{
$As$ are calculated using $AX=YB$. $X$ and $Y$ are assumed.
}
\label{fig3}
\end{figure}

@@

\begin{center}
\begin{figure}
\centering
\includegraphics[width=3.2in]{fig4.eps}
\caption{
The cross correlation of data streams of $(A_{i},B_{i}^{k})$ respectively.
}
\label{fig4}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\centering
\includegraphics[width=3.2in]{fig5.eps}
\caption{
Calculated rotational and translational deviation of $X$ and $Y$ solved using the data in Fig.~\ref{fig2} and Fig.~\ref{fig3}.
}
\label{fig5}
\end{figure}
\end{center}

$B_{i}$ are generated randomly closely around $B_{init}$ using $B_i = B_{init} exp(\mathbf{\widehat{x}})$ and $i$ pose measurements were employed for generating $i$ $A_{i}$ by $A_{i} = YB_{i}X^{-1}$ as shown in Fig.~\ref{fig2} in which a example shows $A$ and $B$ distribution. As a result by applying the above probabilistic method, 8 sequences $(\theta_{A_{i}},\theta_{B_{i}^{k}})$ and $(d_{A_{i}},d_{B_{i}^{k}})$ $ (i=5,\cdots, 100, k=1,\dots,8)$ can be obtained respectively.

If the data streams of $As$ were shifted by $m$ units compared to the data stream $Bs$. The maximum of cross correlation can be used to find the corresponding shift, which is $-m$ shown in Fig.~\ref{fig4}, representing the data stream of $B_{i}^{k}$ has been shifted by -m units with respect to ${A_{i}}$. Therefore, we shift the data stream inversely to recover the correspondence for finding a correct solution satisfying Euclidean-Group invariants.

Using the minimum sum of $||\theta_{A_{i}} - \theta_{B_{i}^{k}}||$ and $||d_{A_{i}} - d_{B_{i}^{k}}||$, we can find the ${B_{i}^{k}}(k=3)$ corresponding to the least sum of errors and then, only a $(X_k,Y_k)$ is the desired solution. In Fig.~\ref{fig5}, as the number of $(A,B)$ pairs increase, the errors of translation and rotations are reduced but when the number comes to a certain value, the errors cannot be reduced furthermore.

\begin{center}
\begin{figure}
\centering
\includegraphics[width=3.2in]{fig6.eps}
\caption{
$Error(R_X)$ distribution as the $As$ and $Bs$ spread ($\sigma(x_i) = 0.1, 0.2, 0.4, 0.6, 0.8, 1, 2$ as shown in Fig.~\ref{fig2})
}
\label{fig6}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\centering
\includegraphics[width=3.2in]{fig7.eps}
\caption{
$Error(R_Y)$ distribution as the $As$ and $Bs$ spread ($\sigma(x_i) = 0.1, 0.2, 0.4, 0.6, 0.8, 1, 2$ as shown in Fig.~\ref{fig2})
}
\label{fig7}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\centering
\includegraphics[width=3.2in]{fig8.eps}
\caption{
$Error(t_X)$ distribution as the $As$ and $Bs$ spread ($\sigma(x_i) = 0.1, 0.2, 0.4, 0.6, 0.8, 1, 2$ as shown in Fig.~\ref{fig2})
}
\label{fig8}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\centering
\includegraphics[width=3.2in]{fig9.eps}
\caption{
$Error(t_Y)$ distribution as the $As$ and $Bs$ spread ($\sigma(x_i) = 0.1, 0.2, 0.4, 0.6, 0.8, 1, 2$ as shown in Fig.~\ref{fig2})
}
\label{fig9}
\end{figure}
\end{center}

In the generation of $B_i = B_{init} exp(\mathbf{\widehat{x}})$, each element $x_j$ of $\mathbf{x} = (x_1,x_2,x_3,x_4,x_5,x_6)^T $ is Gaussian with $N \sim (\mu,\sigma)$. Small disturbances are exerted to the $B_i$ to make the noisy $B_i^{noise} = B_i exp(\mathbf{\widehat{x}}_{noise})$, where each of Lie Algebra element of $\mathbf{x}$ is Gaussian distribution $N \sim (\mu_{noise},\sigma_{noise})$. In Fig.~\ref{fig8},~\ref{fig9},~\ref{fig10} and~\ref{fig11}, $\sigma_{noise}$ is 0.005. As $\sigma$ varies from $0.1$ to $2$, the errors of $R_X$, $R_Y$, $t_X$, and $t_Y$ are reduced as shown in the box-and-whisker plot. There are several outliers not included between the whiskers. The median data can be used as the final solved $X$ and $Y$.

\begin{center}
\begin{figure}
\centering
\includegraphics[width=2.6in]{fig10.eps}
\caption{
The distribution of solved $X$.
}
\label{fig10}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\centering
\includegraphics[width=2.6in]{fig11.eps}
\caption{
The distribution of solved $Y$.
}
\label{fig11}
\end{figure}
\end{center}

>>>>

\begin{center}
\begin{figure}
\centering
\includegraphics[width=3.2in]{fig2.eps}
\caption{
The errors of translation and rotations versus the data stream shift between $A$ and $B$,
}
\label{fig2}
\end{figure}
\end{center}

\begin{figure}
\centering
\includegraphics[width=3.2in]{fig3.eps}
\caption{
The errors of translation and rotations versus noise covariance exerted to the data $B$".
}
\label{fig3}
\end{figure}

@@

\begin{center}
\begin{figure}
\centering
\includegraphics[width=3.2in]{fig4.eps}
\caption{
The solved $X$ (in red) and the actual $X$ (in blue) in 5 trial simulation with noise covariance 0.01 and shift 2.
}
\label{fig4}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\centering
\includegraphics[width=3.2in]{fig5.eps}
\caption{
The solved $Y$ (in red) and the actual $Y$ (in blue) in 5 trial simulation with noise covariance 0.01 and shift 2.
}
\label{fig5}
\end{figure}
\end{center}

$B_{i}$ are generated randomly closely around $\mu$. We get a group of samples $B_i$ from Gaussian distribution over Lie group with a mean $\mu=0 \in G$ and a covariance matrix $\Sigma \in \mathbb{R}^{k \times k}$ as follows.

\begin{IEEEeqnarray}{l}
\delta \in \mathcal{N}(0;\Sigma) \IEEEyessubnumber\label{equ28a}
\\*
x = exp(\delta)\cdot \mu \IEEEyessubnumber\label{equ28b}
\end{IEEEeqnarray}

$i$ pose measurements were employed for generating $i$ $A_{i}$ by $A_{i} = YB_{i}X^{-1}$. As a result by applying the above probabilistic method, 8 sequences $(\theta_{A_{i}},\theta_{B_{i}^{k}})$ and $(d_{A_{i}},d_{B_{i}^{k}})$ $ (i=5,\cdots, 100, k=1,\dots,8)$ can be obtained respectively.

If the data streams of $As$ were shifted by $m$ units compared to the data stream $Bs$. The maximum of cross correlation can be used to find the corresponding shift, which is $-m$, representing the data stream of $B_{i}^{k}$ has been shifted by -m units with respect to ${A_{i}}$. Therefore, we shift the data stream inversely to recover the correspondence for finding a correct solution satisfying Euclidean-Group invariants.

Using the minimum sum of $||\theta_{A_{i}} - \theta_{B_{i}^{k}}||$ and $||d_{A_{i}} - d_{B_{i}^{k}}||$, we can find a ${B_{i}^{k}}$ corresponding to the least sum of errors and then, only a $(X_k,Y_k)$ is the desired solution. In Fig.~\ref{fig2}, as the data stream between $A$ and $B$ shifts increase, the errors of translation and rotations are increased in general.

Small disturbances are exerted to the $B_i$ to make the noisy $B_i^{noise} = B_i exp(\mathbf{\widehat{x}}_{noise})$, where each of Lie Algebra element of $\mathbf{x}){noise}$ is Gaussian distribution $N \sim (\mu_{noise},\sigma_{noise})$. In Fig.~\ref{fig3}, As $\sigma_{noise}$ varies from $0.01$ to $0.08$, the errors of $R_X$, $R_Y$, $t_X$, and $t_Y$ are increased as shown in the box-and-whisker plot. There are several outliers not included between the whiskers. The median data can be used as the final solved $X$ and $Y$. Fig.~\ref{fig4} and Fig.~\ref{fig5} show the solved ($X$,$Y$) in blue and actual ($X$,$Y$) in red in coordinate frame.
